Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013

### 2023-10-31 DraftFour.qmd
Draft Four for real

*(last updated 10/07/2023)*

@@

## **Plot 1: Price vs Length of Stay and Linear Regression Statistical Test**

```{r, include = FALSE}
#| echo: false
# install.packages("readr")
# install.packages("xtable")
library(readr)
library(dplyr)
library(xtable)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
data_set <- read_csv("Hospital_Inpatient_Discharges__SPARCS_De-Identified___2013.csv", show_col_types = FALSE)

cleaned_data <- na.omit(data_set)

@@

```{r}
#| echo: false
y <- cleaned_data$`Total Charges`
```

```{r, results='asis'}
#| echo: false
length_of_stay <- strtoi(cleaned_data$`Length of Stay`)

@@

```
<p align = "center">
[Figure 1a: Length of Stay on Price Regression Dotplot]
</p>

```{r, results='asis'}
#| echo: false
table_lmfs <- xtable::xtable(lmfs, comment = NA, caption = " Figure 1.b: Linear Model Summary")

cat("\\begin{center}\n")
print(table_lmfs, comment = FALSE)
cat("\\end{center}\n")
```
<p align = "center">
[Figure 1b: Table of Linear Regression Modeling Data]
</p>

@@

### Plot Desciption and Inferencing

In addition to the regression analysis, we visualized the relationship between the length of stay and the associated price using a scatter plot with a fitted regression line. The scatter plot provides a clear graphical representation of the positive correlation between these variables. As the length of stay increases, there is a discernible upward trend in price. The regression line, which is based on the linear regression model we performed, further accentuates this trend. It serves as a useful tool for illustrating the direction and strength of the relationship, making it easier to interpret the practical implications of our findings. This visualization reinforces the statistical significance we observed in our analysis and enhances our understanding of the relationship between patient length of stay and healthcare costs for patients in the state of New York in 2013.

@@

## **Plot 2: Boxplot of Total Costs**

```{r}
#| echo: false
cleaned_data$"Total Costs"[cleaned_data$"Total Costs" > quantile(cleaned_data$"Total Costs", 0.95)] <- quantile(cleaned_data$"Total Costs", 0.95)

#summary(cleaned_data$"Total Costs")

boxplot(cleaned_data$"Total Costs",
    main = "Box Plot of Total Costs (Outliers Truncated)",
    ylab = "Total Costs",
    horizontal = TRUE
)

```
<p align = "center">
[Figure 2: Total Costs Boxplot]
</p>

### Plot Desciption and Inferencing

The following boxplot refers to our Total Cost data and is representative of our data that has been cleaned to remove outliers that are in our top 5% of data points, meaning that the outliers that are extremely high are cleaned out. In our analysis, we used a horizontal box plot to summarize the distribution of 'Total Costs' in our dataset. The median, located at approximately \$8,247.96, divides the data into two halves, with the interquartile range (IQR) spanning from Q1 at \$4,519.54 to Q3 at \$15,840.81. Outliers, representing data points significantly deviating from the central distribution, are visible. The total cost range extends from \$0.41 to \$45,292.36, showcasing the data's spread. The mean total cost is around \$12,360.20, but outliers can influence this value. The boxplot also is skewed to the right. This visualization provides key insights into our cost structure analysis.

From this we can infer that there are many outliers, however, in the discussion of costs they are heavily spread and that most patients are paying within our IQR but there are many different outliers that spread when we are discussing costs for healthcare.

@@

## **Plot 3: Payment Type Distribution**

```{r, warning = FALSE, fig.height = 15, fig.width = 50}
#| echo: false
# Set the margin to include more space at the bottom
par(mar = c(5, 4, 4, 2) + 0.1)
par(cex.main = 5 )
cleaned_data$`Payment Typology 1` <- as.factor(cleaned_data$`Payment Typology 1`)
payments <- table(cleaned_data$`Payment Typology 1`)
pie(payments, main = "Payment Type Distribution", col = rainbow(length(payments)), labels = NA)
legend(1, 1, 1, legend = levels(cleaned_data$`Payment Typology 1`), fill = rainbow(length(payments)), cex = 3)

```
<p align = "center">
[Figure 3: Pie Chart of Payment Distribution]
</p>

### Plot Desciption and Inferencing

The following piechart identifies the payment type distribution for patients in New York in 2013. As we can observe, most patients are using Medicare as a way to pay for their medical bills followed by Medicaid. These government programs are important to New York residents and provides important data on the impact of healthcare programs. The exact percentagse are Medicaid at 59.7% and Medicaid at 26.7%, followed by Private Insurance at around 10%. This information reveals how important the impact of governmental insurance programs are to individuals in New York.

## **Plot 4: Trends in Total Charges and Length of Stay**

```{r warning = FALSE}
#| echo: false

plot(cleaned_data$`Length of Stay`, cleaned_data$`Total Charges`, type = "l", col = "blue", xlab = "Length of Stay", ylab = "Total Charges", main = "Trends in Total Charges and Length of Stay")

lines(cleaned_data$`Birth Weight`, cleaned_data$`Total Costs`, col = "red")

legend("topright", legend = c("Total Charges", "Total Costs"), col = c("blue", "red"), lty = 1)

grid()
```
<p align = "center">
[Figure 4:Trends of Total Charges and Legnth of Stay ]
</p>

### Plot Desciption and Inferencing

The plotted data and corresponding projections unmistakably depict a consistent total cost profile, irrespective of variations in both the length of stay and total charges. This apparent lack of correlation between the length of stay and associated costs prompts a deeper inquiry into the potential contributing factors. It would be important to explore the influence of fixed operational costs, negotiated contractual agreements, and astute cost management strategies that may explain this observed financial consistancy between the costs for a hospital and for its patients

## **Plot 5: Barplot of Age Group Distribution of Patients**

```{r}
#| echo: false
ageGroups <- table(cleaned_data$`Age Group`)
barplot(ageGroups,
    main = "Age Group Distribution", xlab = "Age Group",
    ylab = "Frequency", col = "green", border = "black", ylim = c(0, 300000)
)

```
<p align = "center">
[Figure 5: Age Group Distribution of Patients in New York]
</p>

### Plot Desciption and Inferencing

Another important piece of data that we wanted to observe is the amount of patients from each age group of the population. The data is divided into five segmests 0-17, 18-29, 30-49, 50-69, and 70-older. As we can see there is an upward trend of the amount of patients as the ages of the patients increases, although there is a small decrease between 0-17 and 8-29. The largest frequency if the 70-older age bucket which has around 289248 compared to 18-29 with our smallest frequency of 53009.This increase in older patients reveals the impact of older populations in New York and the necesity to increase health care efforts towards older populations.

## Plot 6: Stacked Bar Chart by Gender and Race

```{r}
#| echo: false
# install.packages("ggplot2")
library(ggplot2)

plot7 <- ggplot(cleaned_data, aes(x = Gender, fill = Race)) +
  geom_bar() +
  labs(
    title = "Stacked Bar Chart by Gender and Race",
    x = "Gender",
    y = "Count"
  ) +
  scale_fill_manual(
    values = c("White" = "lightblue", "Black" = "lightcoral", "Other" = "lightgreen"),
    breaks = c("White", "Black", "Other"),
    labels = c("White", "Black", "Other"),
    name = "Race"
  ) +
  theme_minimal()

plot7 + ggtitle("Stacked Bar Chart by Gender and Race")

```
<p align = "center">
[Figure 6: Stacked Bar Chart by Race and Gender]
</p>

In the analysis of patient demographics in the year 2013, a bar chart was employed to visually represent the breakdown of patients by gender and further stratify each gender by race. A notable observation from the chart is the significant predominance of female patients over male patients during this period.

Upon closer examination of the male demographic, the distribution reveals a relatively balanced representation between individuals identified as white and those classified as not white. This suggests a relatively even distribution among male patients concerning racial categories. In contrast, the female demographic exhibits a slightly more diverse distribution across racial categories. This observation implies that, among female patients, there is a greater degree of heterogeneity in terms of racial composition compared to their male counterparts.

These findings contribute valuable insights into the gender and racial composition of the patient population in 2013, emphasizing the need for a nuanced understanding of demographic trends within healthcare settings. Further exploration and analysis of these demographic patterns may reveal additional insights relevant to healthcare planning, resource allocation, and the provision of patient-centered care.

## Plot 7: Boxplots on the Total Costs on the Risk of Mortality

@@

```
<p align = "center">
[Figure 7: Boxplots on Total Cost and Mortality]
</p>

In Figure 7, our objective was to assess the central tendency of total hospital costs across different levels of Risk of Mortality. Employing separate box plots for each severity category allowed us to discern distinct patterns in the distribution of total costs associated with varying degrees of mortality risk. Notably, when focusing on Extreme cases of mortality, a clear trend emerged---median total costs were significantly higher, accompanied by a broader spread in the distribution. This observation implies that patients facing an Extreme risk of mortality not only incur higher median costs but also exhibit greater variability in the financial implications of their healthcare, suggesting a more diverse range of medical interventions and resource utilization.

@@

## Plot 8: Violin Plot Comparing New York City and Western New York's Severity of Illness

@@

```
<p align = "center">
[Figure 8: NYC and Western NY Severity of Illness Comparsion ]
</p>

@@

Figure 8 delves into a detailed breakdown of hospital patients, distinguishing between those originating from New York City (NYC) and Western New York (WNY). The focus is on the distribution of patients' APR severity codes, measured on a 1 to 4 scale (1 being mild, 2 being moderate, 3 being serious, and 4 being extreme). Notably, the violin plot reveals a higher frequency of APR severity code 2 assignments for patients from NYC compared to WNY. This divergence prompts exploration into potential variations in labeling practices between the two regions. However, beyond this distinction, the overall shapes of the violin distributions appear similar, suggesting a general alignment in severity profiles. This observation implies a degree of consistency in patient conditions based on APR severity codes, despite the regional differences in labeling practices. Understanding such variations is crucial for refining medical coding precision and ensuring uniformity in patient severity assessments across diverse geographical contexts.

@@

## Plot 9: Distribution of APR Severity of Illness for Medicaid Patients

@@

```
<p align = "center">
[Figure 9: APR Severity of Illness for Medicaid Patients]
</p>

In our examination of Figure 9, our focus shifted toward a specific subset of patients---those under Medicaid care. Medicaid, a health program designed to support individuals classified as economically disadvantaged, prompted our investigation into the severity of diagnoses within this demographic. Our objective was to discern whether patients under Medicaid receive comparable attention and care in contrast to their counterparts outside of the program.

@@

## Plot 10: Facet Density Plots of Total Cost per Age-Group Buckets

@@

gg + scale_y_continuous(labels = scales::number_format(scale = 1e-3)) +
  labs(title = "Density Plot of Total Costs per Age-Group Bucket", x = "Total Costs", y = "Density (in thousands)") +
  theme_minimal()
```
<p align = "center">
[Figure 10: Density Plots of Total Costs per Age-Groups]
</p>

@@

In Figure 10, we analyzed age-specific total costs by charting density plots using a facet grid. For patients under 17, costs skewed right, suggesting lower expenses, potentially due to the overall good health of children. In contrast, as age increases, a broader and more dispersed peak in total costs emerges, indicating that older patients require more extensive and potentially costlier healthcare interventions, such as hospice services. This exploration sheds light on age-related patterns in healthcare costs, guiding strategies for resource allocation and care planning across different life stages.

>>>>

*(last updated 10/30/2023)*

@@

```{r, warning = FALSE, message = FALSE}
#| echo: false
library(RSQLite)
library(readr)
library(dplyr)
library(xtable)

dcon <- dbConnect(SQLite(), dbname = "finalDB.db", timeout = 10)

@@

## Plot 1: Price vs Length of Stay and Linear Regression Statistical Test

```{r, results='asis', warning=FALSE}
#| echo: false
query <- dbSendQuery(dcon,"
SELECT *
FROM '2013data';
")
cleaned_data <- dbFetch(query, -1)
dbClearResult(query)
y <- cleaned_data$`TotalCharges`
length_of_stay <- strtoi(cleaned_data$`LengthofStay`)

@@

```{=tex}
\begin{center}
Figure 1a: Length of Stay on Price Regression Dotplot
\end{center}
```
```{r, results='asis'}
#| echo: false
table_lmfs <- xtable::xtable(lmfs, comment = NA, caption = " Figure 1.b: Linear Model Summary")

cat("\\begin{center}\n")
print(table_lmfs, comment = FALSE)
cat("\\end{center}\n")
```

Table 1: Table of Linear Regression Modeling Data

@@

@@

## Plot 2: Heat Map of Individuals on Medicaid by Race and Borough**

```{r, fig.height = 6, fig.width = 9, message = FALSE, warning = FALSE}
#| echo: false
library(DBI)
library(RSQLite)
library(ggplot2)
library(sf)
library(tigris)
#| echo: false

query <- dbSendQuery(dcon, "
  SELECT `HospitalCounty`, Race, COUNT(*) as count
  FROM `2013data`
  WHERE `HealthServiceArea` = 'New York City' 
    AND Race IN ('Black/African American', 'White')
  GROUP BY `HospitalCounty`, `Race`
")

data <- dbFetch(query, -1)

ggplot(data, aes(x = `HospitalCounty`, y = `Race`, fill = count)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "red") +
  labs(title = "Number of Black/Other Race Individuals on Medicaid in NYC", 
       x = "Borough", 
       y = "Race", 
       fill = "Count") +
  theme_minimal()

dbClearResult(query)

# Query the data
query <- dbSendQuery(dcon,"
  SELECT `HospitalCounty`, Race, COUNT(*) as count
  FROM `2013data`
  WHERE `HealthServiceArea` = 'New York City' 
    AND Race IN ('Black/African American', 'White')
  GROUP BY `HospitalCounty`, `Race`
"
)
data <- dbFetch(query, -1)

dbClearResult(query)

# Retrieve the NYC boroughs shape data and filter for the five boroughs
options(tigris_use_cache = TRUE)

# Retrieve the NYC boroughs shape data and filter for the five boroughs
ny_counties <- tigris::counties(state = "NY", cb = TRUE) %>%
  st_as_sf()

nyc_boroughs <- ny_counties[ny_counties$NAME %in% c("Bronx", "Kings", "Manhattan", "Queens", "Richmond"), ]

# Merge the data with the nyc_boroughs spatial object
data_sf <- merge(nyc_boroughs, data, by.x = "NAME", by.y = "HospitalCounty")

# Compute the centroids for the NYC boroughs for plotting circles
data_sf$centroid <- st_centroid(st_geometry(data_sf))
```

```{=tex}
\begin{center}
Figure 2: Individuals on Medicaid by Race and Borough
\end{center}
```
\newpage
## Plot 3: Map of Individuals on Medicare by Race**

```{r, warning = FALSE}
#| echo: false
# Plotting side-by-side maps
ggplot(data_sf) +
  geom_sf(aes(fill = NAME), color = "grey60", size = 0.5) +  # Borough fill
  geom_point(aes(x = st_coordinates(centroid)[, "X"], 
                 y = st_coordinates(centroid)[, "Y"], 
                 size = count, 
                 color = Race), 
             alpha = 0.7, show.legend = "point") +  # Plot circles based on count, color-coded by Race

  # Faceting for each race
  facet_wrap(~Race, ncol = 2) +

  # Custom color scale
  scale_color_manual(values = c("Black/African American" = "blue", "White" = "red"), name = "Race") +
  scale_size_continuous(name = "Count", breaks = c(500, 1000, 1500, 2000)) +  # Adjust the size scale for circles

  # Title and subtitles
  labs(title = "Number of Black vs. White Individuals on Medicaid in NYC Boroughs",
       subtitle = "Size of point indicates count, color indicates race") +

  # Minimal theme and customization
  theme_minimal() +
  theme(legend.position = "right",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank())

```{=tex}
\begin{center}
Figure 3: Map of NYC displaying number of individuals on Medicaid by Borough
\end{center}
```
## Plot Description and Inferencing

@@

## Plot 4: Waffle Plot of Severity of Illness by Race**

```{r}
#| echo: false
library(waffle)
library(patchwork)
query <- dbSendQuery(dcon,"
SELECT Race, APRSeverityofIllnessCode FROM '2013data';
                     ")
IllnessCodes <- dbFetch(query, -1)
dbClearResult(query)

waffle_data1 <- data.frame(count = table(IllnessCodes$APRSeverityofIllnessCode[IllnessCodes$Race == "Black/African American"])/2500)
waffle_data2 <- data.frame(count = table(IllnessCodes$APRSeverityofIllnessCode[IllnessCodes$Race == "White"])/5000)

layout(matrix(c(1, 2), nrow = 1))

plot1 <- waffle(waffle_data1, rows = 8, size = .5, 
            colors = c("#FFEDA0", "#FEB24C", "#FC4E2A", "#BD0026"), title = "Black/African Americans")
plot2 <- waffle(waffle_data2, rows = 8, size = .5, 
            colors = c("#FFEDA0", "#FEB24C", "#FC4E2A", "#BD0026"), title = "White")

arrange.plots <- plot1 + theme(plot.title = element_text(size = 10)) + plot2 + theme(plot.title = element_text(size = 10))
arrange.plots
```
\begin{center}
Figure 4: Waffle Plots Depicting Frequencies of APR Codes 
\end{center}

## Plot Description and Inferencing
In the preceding graphical representation, we have visualized the distribution of patients based on their racial backgrounds across the various APR Severity of Illness Codes. These codes are categorized on a scale from 1 to 4, with higher values indicating increased severity. The observed trend indicates that patients of White ethnicity tend to be associated with higher severity APR codes, potentially implying a discrepancy in the prioritization of patient care between White and African American populations.

\newpage
## Plot 5: Barplots of Average Total Charges by Race 2013 vs 2021

```{r, fig.height = 7, fig.width = 5}
#| echo: false
library(ggplot2)
library(patchwork)

pregnant_womenQ <- dbSendQuery(dcon, "
    SELECT Race, TotalCharges
    FROM '2013data'
    WHERE APRMDCCode == 14 OR APRMDCCode == 15;")
pregnant_womenDF = dbFetch(pregnant_womenQ, -1)
dbClearResult(pregnant_womenQ)

plot_race2013 <- ggplot(pregnant_womenDF) + 
  aes(x = Race, y = TotalCharges) +
  stat_summary(fun = "mean", geom = "bar", fill = "salmon") +  # Calculate and plot averages
  labs(x = "Race", y = "Average Total Charges", title = "Average Total Charge by Race in 2013") +  # Customize axis labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 7))  # Rotate x-axis labels for

pregnant_womenQ2 <- dbSendQuery(dcon, "
    SELECT Race, TotalCharges
    FROM '2021data'
    WHERE APRMDCCode == 14 OR APRMDCCode == 15 AND Race != 'Multi-racial';")
pregnant_womenDF2 = dbFetch(pregnant_womenQ2, -1)
dbClearResult(pregnant_womenQ2)

plot_race2021 <- ggplot(pregnant_womenDF2) + 
  aes(x = Race, y = TotalCharges) +
  stat_summary(fun = "mean", geom = "bar", fill = "violet") +  # Calculate and plot averages
  labs(x = "Race", y = "Average Total Charges", title = "Average Total Charge by Race in 2021") +  # Customize axis labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 7))  # Rotate x-axis labels for

combined_plot_race <- plot_race2013 + plot_race2021
combined_plot_race

```
\begin{center}
Figure 5: Barplots of Average Total Charges by Race in 2013 and 2021
\end{center}
## Plot Description and Inferencing
In figure 5, the bar plot illustrates a compelling contrast in average total charges for hospital care among different racial groups. Notably, it highlights that individuals who identify as Black and those categorized under the "Other Races" group experience significantly higher average total charges compared to their White counterparts. This disparity in healthcare costs sheds light on the existing inequalities within the healthcare system, prompting a critical examination of the factors contributing to these disparities and the potential need for targeted interventions to address them. We see that in 2021, post the COVID-19
pandemic, this disparity between average total charges of Black patients and White patients
increased, showing that the pandemic potentially increased already present disparity in healthcare.
\newpage
## Plot 6: Boxplots on the Total Costs on the Risk of Mortality

@@

```{=tex}
\begin{center}
Figure 6: Boxplots on Total Cost and Mortality
\end{center}
```
## Plot Description and Inferencing

In Figure 6, our objective was to assess the central tendency of total hospital costs across different levels of Risk of Mortality. Employing separate box plots for each severity category allowed us to discern distinct patterns in the distribution of total costs associated with varying degrees of mortality risk. Notably, when focusing on Extreme cases of mortality, a clear trend emerged---median total costs were significantly higher, accompanied by a broader spread in the distribution. This observation implies that patients facing an Extreme risk of mortality not only incur higher median costs but also exhibit greater variability in the financial implications of their healthcare, suggesting a more diverse range of medical interventions and resource utilization.

@@

## Plot 7: Violin Plot Comparing New York City and Western New York's Severity of Illness

@@

\begin{center}
Figure 7: NYC and Western NY Severity of Illness Comparsion
\end{center}

@@

Figure 7 delves into a detailed breakdown of hospital patients, distinguishing between those originating from New York City (NYC) and Western New York (WNY). The focus is on the distribution of patients' APR severity codes, measured on a 1 to 4 scale (1 being mild, 2 being moderate, 3 being serious, and 4 being extreme). Notably, the violin plot reveals a higher frequency of APR severity code 2 assignments for patients from NYC compared to WNY. This divergence prompts exploration into potential variations in labeling practices between the two regions. However, beyond this distinction, the overall shapes of the violin distributions appear similar, suggesting a general alignment in severity profiles. This observation implies a degree of consistency in patient conditions based on APR severity codes, despite the regional differences in labeling practices. Understanding such variations is crucial for refining medical coding precision and ensuring uniformity in patient severity assessments across diverse geographical contexts.

@@

## Plot 8: Distribution of APR Severity of Illness for Medicaid Patients

@@

\begin{center}
Figure 8: APR Severity of Illness for Medicaid Patients
\end{center}
## Plot Description and Inferencing

In our examination of Figure 8, our focus shifted toward a specific subset of patients---those under Medicaid care. Medicaid, a health program designed to support individuals classified as economically disadvantaged, prompted our investigation into the severity of diagnoses within this demographic. Our objective was to discern whether patients under Medicaid receive comparable attention and care in contrast to their counterparts outside of the program.

@@

## Plot 9: Facet Density Plots of Total Cost per Age-Group Buckets

@@

gg + scale_y_continuous(labels = scales::number_format(scale = 1e-3)) +
  labs(title = "Density Plot of Total Costs per Age-Group Bucket", x = "Total Costs", y = "Density (in thousands)") +
  theme_minimal()
```

```{=tex}
\begin{center}

Figure 9: Density Plots of Total Costs per Age-Groups

\end{center}
```
## Plot Description and Inferencing

In Figure 9, we analyzed age-specific total costs by charting density plots using a facet grid. For patients under 17, costs skewed right, suggesting lower expenses, potentially due to the overall good health of children. In contrast, as age increases, a broader and more dispersed peak in total costs emerges, indicating that older patients require more extensive and potentially costlier healthcare interventions, such as hospice services. This exploration sheds light on age-related patterns in healthcare costs, guiding strategies for resource allocation and care planning across different life stages.

## Plot 10: Pie Charts of Payment Type by Race
```{r}
#| echo: false
library(ggplot2)
library(gridExtra)
library(patchwork)

paymentTypeAndRaceQ <- dbSendQuery(dcon, "
                                    SELECT Race, PaymentTypology1 FROM '2013data' WHERE Race != 'Unknown';")
paymentTypeAndRaceDF <- dbFetch(paymentTypeAndRaceQ, -1)
dbClearResult(paymentTypeAndRaceQ)
str(paymentTypeAndRaceDF)

pie_charts <- lapply(unique(paymentTypeAndRaceDF$Race), function(race) {
  data_subset <- subset(paymentTypeAndRaceDF, Race == race)
  pie_chart <- ggplot(data_subset, aes(x = "", fill = PaymentTypology1)) +
    geom_bar(width = 1) +
    coord_polar("y") +
    ggtitle(race) +
    theme_void() +
    scale_fill_brewer(palette = "Set3") +
    theme(legend.position = ifelse(race == 'Black/African American', "left", "none"),
          axis.text = element_text(size = 0),
          legend.text = element_text(size = 5)) +
    labs(fill = "Payment Type")

  return(pie_chart)
})
pie_charts[[1]] + pie_charts[[2]] + pie_charts[[3]] + plot_layout(ncol = 1)
```
\begin{center}
Figure 10: Pie Charts on Payment Type by Race
\end{center}

@@
